Interoception Scale - Data Cleaning

### 2024-11-30 study1/analysis/1_cleaning.qmd
add TODO in cleaning
@AnafNeves @EmmaLBenn @maisiebennett

::: panel-tabset
## Summary

-The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.

## Age and Gender

```{r p_demographics_age_gender}
#| warning: false

p_age <- estimate_density(df$Age) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28) +
  geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),)

@@

## Education

@@

## Ethinicity

@@

## Country of Residence

```{r p_demographics_country}
#| warning: false

p_cou <- df |>
 ggplot(aes(x = Country)) +
 geom_bar(aes(fill = Country)) +
 scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
 scale_fill_viridis_d(guide = "none") +
 labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
 theme_modern(axis.title.space = 15) +
 theme(
   plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
   plot.subtitle = element_text(size = rel(1.2), vjust = 7),
   axis.text.y = element_text(size = rel(1.1)),
   axis.text.x = element_text(size = rel(0.7), angle = 45, hjust = 1),
   axis.title.x = element_blank())

p_cou
```

```{r p_demographics_map}
#| warning: false

p_map <- df |>
  mutate(Country = case_when(
    Country=="United States"~ "USA",
    Country=="United Kingdom" ~ "UK",
    TRUE ~ Country
  ))|>
  dplyr::select(region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  # mutate(n = replace_na(n, 0)) |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )

p_map
```
:::

```{r p_summary}
#| warning: false

p_map 
p_age 
p_edu
```

@@

```{r}
#| warning: false

write.csv(df, "../data/data_participants.csv", row.names = FALSE)
```

>>>>

::: panel-tabset

### Summary

- The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.

**TODO**
- The age plot code should be streamlined (there is no need to compute estimate_density)
- Education: add in the preprocessing a manual reassignment of some of the "Other" manual inputs to our categories (and put Other if not in the categories)
- We can merge the edu and student plot by having student be a "color" aesthethic 
- Make Pie chart for ethnicity (see doggonogo for example). 
- Ethnicity: manually check the others and either assign them to the correct category or put them in "Other"

### Age and Gender

```{r p_demographics_age_gender}
p_age <- estimate_density(df$Age) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28, position="identity", alpha=0.5) +
  geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),)

@@

### Education

@@

### Ethinicity

@@

### Country of Residence

```{r p_demographics_map}
p_map <- df |>
  mutate(Country = case_when(
    Country=="United States"~ "USA",
    Country=="United Kingdom" ~ "UK",
    TRUE ~ Country
  ))|>
  dplyr::select(region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  # mutate(n = replace_na(n, 0)) |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )

p_map
```

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```

:::

```{r p_summary}
p_map 
p_age 
p_edu
```

@@

```{r}
write.csv(df, "../data/data_participants.csv", row.names = FALSE)
```
